---
title: "Climate Action Plan 2021-2023 (Visualisation)"
description: |
author:
  - name: Temur Gugushvili 
    url: https://temurgugushvili.ge/
    affiliation: Ivane Javakhishvili Tbilisi State University
    affiliation_url: https://www.tsu.ge/
date: 07-09-2021
preview: image/preview.gif
output:
  distill::distill_article:
    self_contained: false
    toc: true
    toc_depth: 2
    toc_float: true
slug: gugushvili
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(ggplot2)
library(tidyverse)
library(viridis)
library(collapsibleTree)
library(treemapify)
library(collapsibleTree)

```

The project team developed visualization as a side project based on the 2021-2023 Action Plan of Georgia’s 2030 Climate Strategy. The interactive visualization explores responsible institutions for the action plan activities and shows how activities are supported and by how much. 

Some of the findings you can see [here](https://ndctracker.netlify.app/posts/ndctracker/); rest expore by yourself and share with us.

```{r  fig.height = 6, fig.width = 9, dev.args=list(bg='transparent', pointsize=10)}

                                                
ClimateAction <- readr::read_csv("/Users/macbook/Documents/research project/fol_2021/ndcTracker/RNDCTracker/Data/ClimateAction.csv",
                                 col_types = cols(Goal = "c",
                                                  Objective = "c",
                                                  Activity = "c",
                                                  Institution = "c",
                                                  Abbreviation = "c",
                                                  Budget = "c",
                                                  Type_origin = "c",
                                                  Type = "c",
                                                  amount = "n",
                                                  Organization = "c"))



ClimateActionT <- ClimateAction %>%
  filter(amount > 0) %>%
  group_by() %>%
  mutate(Sum = sum(amount)) %>%
  ungroup() %>%
  mutate(Per = amount/Sum*100) 


collapsibleTreeSummary(
  ClimateActionT,
  hierarchy = c("Goal","Institution", "Type", "amount", "Activity"),
  width = 1500,
  zoomable = TRUE,
  linkLength = 350,
  fontSize = 13,
  root = "NDC",
  attribute = "Per",
  tooltip = TRUE,
  maxPercent = 71.5
  )

```

The [data](https://github.com/Temurgugu/RNDCTracker/blob/main/Data/ClimateAction.csv) and [code](https://github.com/Temurgugu/RNDCTracker/blob/main/ndcTracker_cap_all.R) is available at github. 

